Self Regulation Ontology Retest Analyses

### 2018-06-07 code/SRO_Retest_Analyses.Rmd
updated analyses for ranking tasks for meaningful variables only

We reduce the list of task measures to a list of one per task by averaging only the raw measures from all the trials in a task. We chose to reduce the information in this manner to avoid any bias stemming from differential amount of interest and procedures applied to certain tasks over others (e.g. a task can have over 10 measures because it has multiple conditions and we have chosen to fit DDM's for specific conditions while another might only have 2 due to our relative inexperience and lack of interest in it). We check whether the number of trials in a task has a significant effect on these average reliabilities of raw measures as well.

We filter out the DDM parameters and measures for specific contrasts. Note that this does leave some tasks with measures that are model fits and/or for specific conditions (because at least the current datasets do not include measures that are based on all the trials **and** are raw though I could dive in to variables_exhaustive for such measures. For example the average relialibility for Kirby is based on three discount rates for specific conditions.). Here's the order of tasks by mean reliability sorted for ICC and then Spearman's $\rho$.

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task') %>%
  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv') %>%
  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2) %>%
  group_by(task_name) %>%
  summarise(median_icc = median(icc),
            median_spearman = median(spearman),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975),
            min_spearman = min(spearman),
            max_spearman = max(spearman),
            num_measures = n()/1000,
            mean_num_trials = round(mean(num_all_trials)))%>%
  arrange(-median_icc, -median_spearman)

```{r}
tmp = tmp%>%
  select(-median_spearman, -min_spearman, -max_spearman) %>%
  mutate(task_name = gsub("_", " ", task_name),
         task_name = gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", task_name, perl=TRUE))

@@

### Meaningful variables

```{r}

@@

Does number of items in a task have a significant effect on the average ICC of (mostly) raw measures for all trials from a task? No. (no effect on Spearman either)

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task') %>%
  # left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
  left_join(boot_df[,c("dv", "spearman","icc")], by='dv') %>%
  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2)

@@

@@

For this example we look at the retest reliability of the three dependent measures (average accuracy, median response time, total score) from the hierarchical rule task with 360 trials. Here is a graph of how the point estimates of the retest reliability changes for each of the dependent measures using different numbers of trials to estimate them. While the reliability estimate for each of the variables respectively are ..., ... and ... using all of the trials, these values are independent of number of trials used in the task for only certain variables. Based on this analysis researchers might decide to use a version of the task with fewer trials or only measures with consistently high reliability estimates.

Example task: three by two

>>>>

We reduce the list of task measures to a list of one per task by averaging only the measures that are extracted and used from these tasks in the literature. We call these the 'meaningful measures.'

```{r}
meaningful_vars = read.table('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/meaningful_vars.txt')
meaningful_vars = as.character(meaningful_vars$V1)

tmp = as.character(unique(lit_review$dv)[which(unique(lit_review$dv) %in% meaningful_vars == FALSE)])
tmp = tmp[-grep('survey', tmp)]

meaningful_vars = c(meaningful_vars, tmp)
meaningful_vars = sort(meaningful_vars)
```

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task',
         dv %in% meaningful_vars) %>%
  left_join(boot_df[,c("dv", "icc")], by = 'dv') %>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2) %>%
  group_by(task_name) %>%
  summarise(median_icc = median(icc),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975),
            num_measures = n()/1000,
            mean_num_trials = round(mean(num_all_trials)))%>%
  arrange(-median_icc)

tmp %>%
  datatable() %>%
  formatRound(columns=c('median_icc','icc_2.5','icc_97.5'), digits=3)
```

```{r}
tmp = tmp%>%
  mutate(task_name = gsub("_", " ", task_name),
         task_name = gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", task_name, perl=TRUE))

@@

@@

Does number of items in a task have a significant effect on the average ICC of meaningful measures for all trials from a task? No.

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task',
         dv %in% meaningful_vars) %>%
  left_join(boot_df[,c("dv", "icc")], by = 'dv') %>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2)

@@

```{r warning=FALSE, message=FALSE}
tmp %>%
  ggplot(aes(num_all_trials, icc))+
  geom_point()+
  geom_smooth(method="lm")+
  theme_bw()+
  xlab("Number of trials")+
  ylab("ICC")
```

@@

For this example we look at the retest reliability of dependent measures from the threebytwo with >400 trials. Here is a graph of how the point estimates of the retest reliability changes for each of the dependent measures using different numbers of trials to estimate them.
